---
title: "Finalized Figure Example"
author: "Camila Vargas"
date: "8/1/2018"
output: html_document
---

The following scrip descibes how to obtain the ranking and time serie plots for one country. Next steps are to add this in a for loop (or purr) of each country.

# Set up
```{r}
library(tidyverse)
library(plotly)
library(readr)

```

# Scores Timeseries 

## Data

Score Description short version from methods

AO   | Opportunity for small-scale fishers to supply catch to their families, community or local market.
BD   | Conservation status of native marine species and key habitats
CS   | Condition of coastal habitats that store and sequester atmospheric carbon
CW   | Degree to which oceans are free of contaminants such as chemicals, excessive nutrients, human pathogens, and trash
LE   | Coastal and ocean-dependent livelihoods (job quantity and quality) and economies (revenues) produced by marine sectors
CP   | Amount of protection provided by marine and coastal habitats serving as natural buffers against incoming waves
FP   | Sustainable harvest of seafood from wild-caught fisheries and mariculture 
NP   | Natural resources that are sustainably extracted from living marine resources
SP   | Conservation status of iconic species and geographic locations that contribute to cultural identity
TR   | Value people have for experiencing and enjoying coastal areas and attractions


```{r}
scores <- read.csv('https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/scores.csv') %>%
  rename(abb = "goal")

#Goals Description according to "short version" 

goals <-  data.frame(goal = c("Index", 
                              "Artisanal Opporunities", 
                              "Biodiversity",
                              "Carbon Storage",
                              "Clean Waters", 
                              "Livelihoods and Economies",
                              "Coastal Protection", 
                              "Food Provision",
                              "Natural Products", 
                              "Sense of Place", 
                              "Tourism and Recreation"), 
                     abb = c("Index", 
                             "AO", 
                             "BD", 
                             "CS",
                             "CW", 
                             "LE", 
                             "CP", 
                             "FP", 
                             "NP", 
                             "SP", 
                             "TR"), 
                     description = c("Overall Ocean Health Index score", 
                                     "Opportunity for small-scale fishers to supply <br> catch to their families, community or local market", 
                                     "Conservation status of native marine species and key habitats", 
                                     "Condition of coastal habitats that store and <br> sequester atmospheric carbon", 
                                     "Degree to which oceans are free of contaminants such as  <br> chemicals, excessive nutrients, human pathogens, and trash", 
                                     "Coastal and ocean-dependent livelihoods (job quantity and quality) <br> and economies (revenues) produced by marine sectors", 
                                     "Amount of protection provided by marine and coastal habitats <br> serving as natural buffers against incoming waves", 
                                     "Sustainable harvest of seafood from wild-caught <br> fisheries and mariculture ", 
                                     "Natural resources that are sustainably extracted <br> from living marine resources", 
                                     "Conservation status of iconic species and geographic <br> locations that contribute to cultural identity", 
                                     "Value people have for experiencing and enjoying <br> coastal areas and attractions")) 


scores_description <- scores %>% 
  left_join(goals, by= "abb") %>% 
  mutate(label = ifelse(year == max(year), as.character(abb), NA_character_))




```



## Filter for one country
In this case Chile
**Note** Here I also filter for the score of each goal and the the Index (no sub-goals included here)

```{r}
chile <- scores_description %>% 
  dplyr::filter(region_id=='224') %>% 
  dplyr::filter(dimension == 'score') %>% 
  dplyr::filter(abb %in% c('AO', 'BD', 'CP', 'CS', 'CW', 'FP', 'Index', 'LE', 'NP', 'SP', 'TR'))
```

## Plot

```{r}
chile_plot <- ggplot(data = chile, aes(x = year, y = score, color= goal)) +
  geom_line(size = 1)+
  geom_point(aes(text = paste("Goal: ", goal, "<br>Year:", year, "<br>Score:", score, "<br>Description: ", description)), size = 2)+
  theme_light()+
  geom_line(data=subset(chile, goal == "Index"), size= 1.8)+ #changes the thinkness of the index lne and points respectively
  geom_point(data=subset(chile, goal == "Index"), size= 2)+
  scale_x_continuous(breaks = seq(2012, 2018, 1))+
  labs(x="Year", y="Score", color = "Goal")+ #color= Goal changes the title of the key
  #ggtitle("Scores Timeseries")+
  #scale_colour_brewer(palette = "Spectral")+
  theme(legend.title = element_text(size = 12, color = "black"),
        legend.text = element_text(size = 10),
        legend.key = element_rect(size = 1))+
scale_color_manual(name="Goal", #customize color and key names manually. NOTE code for color don't work
                      labels = c("Artisanal Opporunities",
                                 "Biodiversity",
                                 "Coastal Protection",
                                 "Carbon Storage",
                                 "Clean Waters",
                                 "Food Provision",
                                 "Index",
                                 "Livelihoods and Economies",
                                 "Natural Products",
                                 "Sense of Place",
                                 "Tourism and Recreation"),
                   values = c("Artisanal Opporunities" = "aquamarine3",
                                 "Biodiversity" = "goldenrod1",
                                 "Coastal Protection" = "thistle3",
                                 "Carbon Storage" = "hotpink2",
                                 "Clean Waters" = "tomato2",
                                 "Food Provision" = "sienna2",
                                 "Index" = "black",
                                 "Livelihoods and Economies" = "pink1",
                                 "Natural Products" = "lightcyan4",
                                 "Sense of Place" = "plum4",
                                 "Tourism and Recreation" = "darkseagreen3"))
plot(chile_plot) 
  
#PLOTLY!!
ggplotly(chile_plot, tooltip="text") %>% 
  config(displayModeBar = F) #this allows me to disply only the hover text I assing in geom_point.


```


# Ranking Plot


## Data
In this case the ranking is ploted based on the scores of the most resent assessment 

```{r}
##Data

 rank <- scores %>% 
  dplyr::filter(dimension == "score",
                abb == "Index",
                year == 2018) %>% 
  dplyr::arrange(desc(score)) %>% 
  dplyr::mutate(ranking = seq(1, 222, 1))


```


## Identify the country of interest
One solution to color the bar of the country of interes is to add a column to the data.frame that recognize the country that need to be colored.
In this case I'll try with Chile,
**Note** Think how this will loof like in the for loop

```{r}

rank_color_country <- rank %>% 
  mutate(color= ifelse(region_id== 224, "yes", "no"))

```



## The Plot

```{r}
##histogram

rank_plot <- ggplot(data = rank_color_country, aes(x= ranking, y= score, color=color))+
  geom_bar(aes(fill=color), stat = "identity", width = .2)+
  theme_minimal()+
  ylab("Score")+
  scale_fill_manual(values = c("cadetblue", "seagreen3"))+
  theme(panel.grid = element_blank(),
        legend.position = "none",
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(color = "grey45", vjust = 2)) 
  


plot(rank_plot)
```


## Improving the code with casey's code. 

for website (plotly)

```{r}
chile_plot_2 <- ggplot(chile %>%
                         filter(abb != "Index"),
                       aes(x = year, y = score, color = goal)) +
  geom_line(data = chile %>% 
              filter( abb == "Index"),
            aes(x = year, y = score), size = 1, color = 'gray20', alpha = .9) +
  geom_point(data = chile %>% 
              filter( abb == "Index"),
            aes(x = year, y = score, text = paste("Goal: ", goal, "<br>Year:", year, "<br>Score:", score, "<br>Description: ", description)), size = 1.5, color = 'gray20', alpha = .9)+
  geom_line(aes(group = goal), alpha = .7, size = .5)+
  geom_point(aes(text = paste("Goal: ", goal, "<br>Year:", year, "<br>Score:", score, "<br>Description: ", description)), size = .9)+
    scale_x_continuous(breaks = seq(2012, 2018, 1))+
  labs(x="Year", y="Score", color = "Goal", caption = "Note: Gray line represents the overall region score")+ #caption does not display in plotly
  theme_minimal()+
  scale_color_viridis_d()+
  guides(colour = guide_legend(override.aes = list(size = 3)))

plot(chile_plot_2)

ggplotly(chile_plot_2, tooltip="text") %>% 
  config(displayModeBar = F)


```


for region card (ggplot)

*make the lines thicker

```{r}

chile_plot_3 <- ggplot(chile %>%
                         filter(abb != "Index"),
                       aes(x = year, y = score, color = goal)) +
  geom_line(data = chile %>% 
              filter( abb == "Index"),
            aes(x = year, y = score), size = 1.3, color = 'gray20', alpha = .9) +
  geom_point(data = chile %>% 
              filter( abb == "Index"),
            aes(x = year, y = score, text = paste("Goal: ", goal, "<br>Year:", year, "<br>Score:", score, "<br>Description: ", description)), size = 1.8, color = 'gray20', alpha = .9)+
  geom_line(aes(group = goal), alpha = .7, size = .8)+
  geom_point(aes(text = paste("Goal: ", goal, "<br>Year:", year, "<br>Score:", score, "<br>Description: ", description)), size = 1)+
    scale_x_continuous(breaks = seq(2012, 2018, 1))+
  labs(y="Score", color = "Goal")+ # caption = "Note: Gray line represents the overall region score" caption does not display in plotly
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 30),
        axis.title.x = element_blank()) +
  scale_color_viridis_d()+
  guides(colour = guide_legend(override.aes = list(size = 3)))

plot(chile_plot_3)

ggsave('ts_chile.png', plot = chile_plot_3, device = 'png', path= 'figures/time_series', height = 6, width = 6, dpi = 300)




```



Replacing key by adding names on tom of each line

```{r}

library(ggrepel)

chile_plot_4 <- ggplot(chile %>%
                         filter(abb != "Index"),
                       aes(x = year, y = score, color = goal)) +
  geom_line(data = chile %>% 
              filter( abb == "Index"),
            aes(x = year, y = score), size = 1.3, color = 'gray20', alpha = .9) +
  geom_point(data = chile %>% 
              filter( abb == "Index"),
            aes(x = year, y = score, text = paste("Goal: ", goal, "<br>Year:", year, "<br>Score:", score, "<br>Description: ", description)), size = 1.8, color = 'gray20', alpha = .9)+
  geom_text_repel(data= chile %>% 
                    filter( abb == "Index"),
                    aes(label = label), na.rm=TRUE, nudge_x=-0.1, point.padding = unit(8, "points"), nudge_y = 1, size= 3, segment.color=NA, color = 'gray20')+
  geom_line(aes(group = goal), alpha = .7, size = .8)+
  geom_point(aes(text = paste("Goal: ", goal, "<br>Year:", year, "<br>Score:", score, "<br>Description: ", description)), size = 1)+
    scale_x_continuous(breaks = seq(2012, 2018, 1))+
  labs(y="Score", color = "Goal")+ 
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 30),
        axis.title.x = element_blank(),
        legend.position = "None") +
  geom_text_repel(aes(label = label), na.rm=TRUE, nudge_x= 0.1, point.padding = unit(8, "points"), nudge_y = 0.5, size=3, segment.color=NA) +
  scale_color_viridis_d()+
  guides(colour = guide_legend(override.aes = list(size = 3)))

plot(chile_plot_4)

ggsave('ts_chile.png', plot = chile_plot_4, device = 'png', path= 'figures/time_series', height = 4, width =6 , dpi = 300)




```













