---
title: "Camila's Independent Project"
author: "Camila Vargas"
date: "7/9/2018"
output: html_document
---

#Project Description

Communicate the years of scores by country, how could we do this better: 
www.oceanhealthindex.org/region-scores/scores/samoa and have it on ohi-science.org/ohi-global. Think through the information to be presented (including time series, ranking), so we can migrate it over to where we are. Start off outlining/sketching this out: what do we need and where would it go? Don’t worry about the code and interactivity as a first step, but what kinds of plots and data would we want to display. Then, we’ll work on the code.

Background: goal is migrating information from oceanhealthindex.org over to ohi-science.org/ohi-global. Starting point: static figure of goals through time by country, or country through time by goal. 

Use the scores by year and try to develop something for people who want to learn more about OHI scores, but at a glance. Bringing some of the messaging from oceanhealthindex.org over to ohi-science.org/ohi-global “fluffy in a good way fluffy” - Mel
Or another way of thinking about it could be exploring at the goal, where data is 


**Goal** Present global scores per country and per goal in a usefuel and informaive way.

#Audience
Anyone who want to learn more about the OHI scores but not dive into the data.
People at a country level and/or goal level who wants to be informed by looking into the OHI scores at a glance. 


##Initial Exploration of the data
```{r}
library(tidyverse)
library(plotly)

```



```{r}
##Read in the data that needs to be visualized. 

scores <- read.csv('https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/scores.csv') %>% 
  rename(abb = "goal")


```


Initial findings:

Each country has the "score" data for each goal for every year.

* Each goal has 6 dimensions:
  + Future
  + Pressure
  + Resilence
  + Score
  + Status
  + Trend
  
With this project we are trying to visialize scores for each country, pero goal and per year


Adding goal description to the main data set
 
```{r}
##Creating a dataframe with goal description

goals <-  data.frame(goal = c("Index", "Artisanal Opporunities", "Biodiversity", "Coastal Protection", "Carbon Storage", "Clean Waters", "Food Provision", "Livelihoods and Economies", "Natural Products", "Sense of Place", "Tourism and Recreation"), abb = c("Index", "AO", "BD", "CP","CS", "CW", "FP", "LE", "NP", "SP", "TR"), description = c("Overall Ocean Health Index score", "Measures whether people who need to fish <br> on a small, local scale have the opportunity to do so", "Estimates how successfully the richness <br> and variety of marine life is being maintained", "Measures the condition of coastal habitats <br> that store and sequester atmospheric carbon", "Measures the degree to which oceans are free of chemicals contaminants, <br> excessive nutrients, human pathogens and trash", "Coastal and ocean-dependent livelihoods (job quantity and quality) <br> and economies (revenues) produced by marine sectors", "The amount of protection provided <br> by marine and coastal habitats that safeguard shores", "Measures the amount of seafood captured <br> or raised in a sustainable way", "Measures how sustainably people harvest <br> non-food products from the sea", "The conservation status of iconic species and <br> geographic locations that contribute to cultural identity", "The value people have for experiencing <br> and enjoying coastal areas and attractions")) 

##FIGURE OUT HOW TO EXPORT THE DATAFRAME IN A NICE TABLE!!!!!!


##Add goal description to the score dataframe

scores_description <- scores %>% 
  left_join(goals, by= "abb")

```
 
Actually there is a table with this information in the Methods.
So reading the table with descriptions

```{r}
goals_description <- read.csv('https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/global_supplement/tables/ten_goals.csv')

View(goals_description)

```

But, definitions are too long.

Addapting the goal definitions:

AO: Measures whether people who need to fish on a small, local scale have the opportunity to do so

BD: Estimates how successfully the richness and variety of marine life is being maintained

CS: Measures the condition of coastal habitats that store and sequester atmospheric carbon

CW: Measures the degree to which oceans are free of chemicals contaminants, excessive nutrients, human pathogens and trash

LE: Coastal and ocean-dependent livelihoods (job quantity and quality) and economies (revenues) produced by marine sectors

CP: The amount of protection provided by marine and coastal habitats serving as natural buffers against incoming waves

FP: Measures the amount of seafood captured or raised in a sustainable way.

NP: Measures how sustainably people harvest non-food products from the sea.

SP:The conservation status of iconic species and geographic locations that contribute to cultural identity

TR: The value people have for experiencing and enjoying coastal areas and attractions




```{r}
## Exploration with Chile - Chile data

chile <- scores_description %>% 
  dplyr::filter(region_id=='224') %>% 
  dplyr::filter(dimension == 'score') %>% 
  dplyr::filter(abb %in% c('AO', 'BD', 'CP', 'CS', 'CW', 'FP', 'Index', 'LE', 'NP', 'SP', 'TR'))
```


Traying different versions of the plot- Exploring/learning ggplot

```{r}
##Plot time serie per goal

chile_plot <- ggplot(data = chile, aes(x = year, y = score, color= goal)) +
  geom_line()+
  geom_point()+
  theme_light()+
  labs(title= "Chile", x="Year", y="Score")+
  scale_color_manual(name="Goal", #customize color and key names manually. NOTE code for color don't work
                        labels = c("Artisanal Opporunities", 
                                   "Biodiversity", 
                                   "Coastal Protection", 
                                   "Carbon Storage", 
                                   "Clean Waters", 
                                   "Food Provision",
                                   "Index",
                                   "Livelihoods and Economies", 
                                   "Natural Products", 
                                   "Sense of Place", 
                                   "Tourism and Recreation"), 
                        values = c("AO"="#A50026", 
                                   "BD"="#D73027", 
                                   "CP"="#F46d43", 
                                   "CS"="#FDAE61", 
                                   "CW"="#FEE090",
                                   "FP" = "#E0F3F8",
                                   "Index" = "#000000",
                                   "LE" = "#ABD9E9",
                                   "NP" = "#74ADD1",
                                   "SP" = "#4575B4",
                                   "TR" = "#313695"))
plot(chile_plot)


```


```{r}
chile_plot <- ggplot(data = chile, aes(x = year, y = score, color= goal)) +
  geom_line(size = 1)+
  geom_point(aes(text = paste("Goal: ", goal, "<br>Year:", year, "<br>Score:", score, "<br>Description: ", description)), size = 2)+
  theme_light()+
  geom_line(data=subset(chile, goal == "Index"), size= 1.8)+ #changes the thinkness of the index lne and points respectively
  geom_point(data=subset(chile, goal == "Index"), size= 2)+
  scale_x_continuous(breaks = seq(2012, 2018, 1))+
  labs(x="Year", y="Score", color = "Goal")+ #color= Goal changes the title of the key
  #ggtitle("Scores Timeseries")+
  #scale_colour_brewer(palette = "Spectral")+
  theme(legend.title = element_text(size = 12, color = "black"),
        legend.text = element_text(size = 10),
        legend.key = element_rect(size = 1),
        legend.position = "bottom",
        legend.box = "horizontal")+
scale_color_manual(name="Goal", #customize color and key names manually. NOTE code for color don't work
                      labels = c("Artisanal Opporunities",
                                 "Biodiversity",
                                 "Coastal Protection",
                                 "Carbon Storage",
                                 "Clean Waters",
                                 "Food Provision",
                                 "Index",
                                 "Livelihoods and Economies",
                                 "Natural Products",
                                 "Sense of Place",
                                 "Tourism and Recreation"),
                   values = c("Artisanal Opporunities" = "aquamarine3",
                                 "Biodiversity" = "goldenrod1",
                                 "Coastal Protection" = "thistle3",
                                 "Carbon Storage" = "hotpink2",
                                 "Clean Waters" = "tomato2",
                                 "Food Provision" = "sienna2",
                                 "Index" = "black",
                                 "Livelihoods and Economies" = "pink1",
                                 "Natural Products" = "lightcyan4",
                                 "Sense of Place" = "plum4",
                                 "Tourism and Recreation" = "darkseagreen3"))
plot(chile_plot) 
  
#PLOTLY!!
ggplotly(chile_plot, tooltip="text") %>% 
  config(displayModeBar = F) #this allows me to disply only the hover text I assing in geom_poit.





  
```

Trying colors

```{r}
chile_plot <- ggplot(data = chile, aes(x = year, y = score, color= goal)) +
  geom_line()+
  geom_point()+
  theme_light()+
  labs(title= "Chile", x="Year", y="Score")+
  scale_color_manual(name="Goal", #customize color and key names manually. NOTE code for color don't work
                        labels = c("Artisanal Opporunities", 
                                   "Biodiversity", 
                                   "Coastal Protection", 
                                   "Carbon Storage", 
                                   "Clean Waters", 
                                   "Food Provision",
                                   "Index",
                                   "Livelihoods and Economies", 
                                   "Natural Products", 
                                   "Sense of Place", 
                                   "Tourism and Recreation"), 
                        values = c("AO"="#990033", 
                                   "BD"="#D73027", 
                                   "CP"="#F46d43", 
                                   "CS"="#FDAE61", 
                                   "CW"="#FEE090",
                                   "FP" = "#E0F3F8",
                                   "Index" = "#000000",
                                   "LE" = "#ABD9E9",
                                   "NP" = "#74ADD1",
                                   "SP" = "#4575B4",
                                   "TR" = "#313695"))
plot(chile_plot)


```


Try another country!

```{r}

kiribati <- scores_description %>% 
  dplyr::filter(region_id=='212')%>%
  dplyr::filter(dimension == 'score') %>% 
  dplyr::filter(abb %in% c('AO', 'BD', 'CP', 'CS', 'CW', 'FP', 'Index', 'LE', 'NP', 'SP', 'TR'))


##plot

kiribati_plot <- ggplot(data = kiribati, aes(x = year, y = score, color= goal, label= description)) +
  geom_line(size= 1.2)+
  geom_point()+
  theme_light()+
  labs(title= "Kiribati", x="Year", y="Score")+
  scale_colour_brewer(palette = "RdYlBu")
  
plot(kiribati_plot) 



```

Ploting the highest score: South Georgia and the South Sandwich Islands


```{r}

SGS <- scores_description %>% 
  dplyr::filter(region_id=='89')%>%
  dplyr::filter(dimension == 'score') %>% 
  dplyr::filter(abb %in% c('AO', 'BD', 'CP', 'CS', 'CW', 'FP', 'Index', 'LE', 'NP', 'SP', 'TR'))


##plot

SGS_plot <- ggplot(data = SGS, aes(x = year, y = score, color= goal, label= description)) +
  geom_line(size= 1.2)+
  geom_point()+
  theme_light()+
  labs(title= "South Georgia and the South Sandwich Islands", x="Year", y="Score")+
  scale_colour_brewer(palette = "RdYlBu")
  
plot(SGS_plot) 
ggplotly(SGS_plot)

```

Plot using plotly

```{r}

color_color <- colors()[c("#8DD3C7", "#FFFFB3", "#BEBADA", "#FB8072", "#000000", "#80B1D3", "#FDB462", "#B3DE69", "#FCCDE5", "#D9D9D9", "#BC80BD")]

chile_ply <- plot_ly(chile, x=~year, y=~score, type = "scatter", color = ~goal, 
                     colors = ~Index = "#000000", mode= "lines+markers", hoverinfo = "text",
                     text = ~paste("</br> Goal: ", goal,
                                   "</br> Year: ", year,
                                   "</br> Score: ", score,
                                   "</br> Description: ", description))
  


chile_ply


chile_ply2 <- plot_ly(chile, x=~year, y=~score, type = "scatter", color = ~goal, mode= "lines+markers", hoverinfo = "text",
                     text = ~paste("</br> Goal: ", goal,
                                   "</br> Year: ", year,
                                   "</br> Score: ", score,
                                   "</br> Description: ", description))



chile_ply3 <- plot_ly(chile, x=~year, y=~score, type = "scatter", color = ~goal, colors = c("#8DD3C7", "#FFFFB3", "#BEBADA", "#FB8072", "#000000", "#80B1D3", "#FDB462", "#B3DE69", "#FCCDE5")   , mode= "lines+markers", hoverinfo = "text",
                     text = ~paste("</br> Goal: ", goal,
                                   "</br> Year: ", year,
                                   "</br> Score: ", score,
                                   "</br> Description: ", description))





##"#8DD3C7", "#FFFFB3", "#BEBADA", "#FB8072", "#80B1D3", "#FDB462", "#B3DE69", "#FCCDE5" "#D9D9D9", "#BC80BD"

##'rgb(141,211,199)','rgb(255,255,179)','rgb(190,186,218)','rgb(251,128,114)','rgb(128,177,211)','rgb(253,180,98)','rgb(179,222,105)','rgb(252,205,229)','rgb(217,217,217)','rgb(188,128,189)'

```


More Plotly!
Advance things.. Dropdown?


```{r}

#Data frame: chile - All goals scores + Index score calculated for Chile from 2012 to 2018

View(chile)
colnames(chile) #"abb"   "dimension"   "region_id"   "score"       "year"        "goal"        "description"

chile_test <- chile %>%  
  group_by(year) %>%
  select(-goal, -description) %>% 
  spread(abb, score) 
  
 graph1 <- plot_ly(chile_test, x=~year) %>% 
   add_lines(y = ~Artisanal Opporunities, name= "Artisanal Opporunities") %>%  #, mode= "lines+markers", color = "#8DD3C7")
   add_lines(y = ~Biodiversity, name = "Biodiversity", visible = F)

p1 <- plot_ly(chile_test, x = ~year) %>%
  add_lines(y = ~AO, name = "Artisanal Opporunities") %>% 
  add_lines(y = ~BD, name = "Biodiversity")




```


Ranking plot!!

```{r}

##Data
rank <- scores %>% 
  dplyr::filter(dimension == "score") %>%
  dplyr::filter(abb == "Index") %>% 
  dplyr::filter(year == 2018) %>% 
  dplyr::arrange(desc(score)) %>% 
  dplyr::mutate(ranking = seq(1, 222, 1))


##histogram

rank_plot <- ggplot(data = rank, aes(x= ranking, y= score))+
  geom_bar(stat = "identity", color = "lightblue1", fill = "midnightblue")+
  #geom_bar(data=subset(rank, region_id == 224, fill= "lightblue1"))+
  theme_minimal()+
  theme(panel.grid = element_blank(),
        axis.text.x = element_blank())
  

plot(rank_plot)




```


Exploring a seconf option on how to fill in only the country of interest

```{r}
country_interest <- rank %>% 
  mutate(color= ifelse(region_id== 224, 1, 0)) %>% 
  select(color) %>% 
  list()

rank_plot <- ggplot(data = rank, aes(x= ranking, y= score, fill = country_interest))+
  geom_bar(stat = "identity")+
  theme_minimal()+
  theme(panel.grid = element_blank(),
        axis.text.x = element_blank())

##DID NOT WORK
```








