---
title: "Camila's Independent Project"
author: "Camila Vargas"
date: "7/9/2018"
output: html_document
---

#Project Description

Communicate the years of scores by country, how could we do this better: 
www.oceanhealthindex.org/region-scores/scores/samoa and have it on ohi-science.org/ohi-global. Think through the information to be presented (including time series, ranking), so we can migrate it over to where we are. Start off outlining/sketching this out: what do we need and where would it go? Don’t worry about the code and interactivity as a first step, but what kinds of plots and data would we want to display. Then, we’ll work on the code.

Background: goal is migrating information from oceanhealthindex.org over to ohi-science.org/ohi-global. Starting point: static figure of goals through time by country, or country through time by goal. 

Use the scores by year and try to develop something for people who want to learn more about OHI scores, but at a glance. Bringing some of the messaging from oceanhealthindex.org over to ohi-science.org/ohi-global “fluffy in a good way fluffy” - Mel
Or another way of thinking about it could be exploring at the goal, where data is 


**Goal** Present global scores per country and per goal in a usefuel and informaive way.

#Audience
Anyone who want to learn more about the OHI scores but not dive into the data.
People at a country level and/or goal level who wants to be informed by looking into the OHI scores at a glance. 


##Initial Exploration of the data
```{r}
library(tidyverse)
```



```{r}
##Read in the data that needs to be visualized. 

scores <- read.csv('https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/scores.csv')


##Playing around with Chile
chile <- scores %>% 
  dplyr::filter(region_id=='224')

```


Initial findings:

Each country has the "score" data for each goal for every year.

* Each goal has 6 dimensions:
  + Future
  + Pressure
  + Resilence
  + Score
  + Status
  + Trend
  
With this project we are trying to visialize scores for each country, pero goal and per year

```{r}
## More Ecploration with Chile

chile <- chile %>%
  dplyr::filter(dimension == 'score') %>% 
  dplyr::filter(goal %in% c('AO', 'BD', 'CP', 'CS', 'CW', 'FP', 'Index', 'LE', 'NP', 'SP', 'TR'))


##Plot time serie per goal

ggplot(data = chile, aes(x = year, y = score)) +
  geom_line(aes(color= goal))
  


```






